Online Sequential Monte Carlo smoother for partially observed diffusion processes

### 2017-09-14 TexSubmission/ParisEM.tex
small typo

\section{Conclusions}
This paper presents a new online SMC smoother for partially observed differential equations.
 This algorithm relies on an acceptance-rejection procedure inspired from the recent PaRIS algorithm.
 The main result of the article for practical applications is that the mechanism of this procedure remains valid when the transition density is approximated by a an unbiased positive estimator.
  The proposed procedure therefore extends the PaRIS algorithm to HMMs whose transition density is unknown and can be unbiasedly approximated. The GRand PaRIS algorithm outperforms the existing fixed lag smoother for POD processes of \cite{olsson:strojby:2011}, as it does not introduce any intrinsic and non vanishing bias.
   In addition, numerical simulations highlight a better variance using data from two different models.
   It can be implemented for the class of models for which exact algorithms of \cite{beskos:papaspiliopoulos:roberts:fearnhead:2006} are valids, with a linear complexity in $N$ in the best cases, or at worse in $N^2$.

>>>>

\section{Conclusions}
This paper presents a new online SMC smoother for partially observed differential equations.
 This algorithm relies on an acceptance-rejection procedure inspired from the recent PaRIS algorithm.
 The main result of the article for practical applications is that the mechanism of this procedure remains valid when the transition density is approximated by a an unbiased positive estimator.
  The proposed procedure therefore extends the PaRIS algorithm to HMMs whose transition density is unknown and can be unbiasedly approximated. The GRand PaRIS algorithm outperforms the existing fixed lag smoother for POD processes of \cite{olsson:strojby:2011}, as it does not introduce any intrinsic and non vanishing bias.
   In addition, numerical simulations highlight a better variance using data from two different models.
   It can be implemented for the class of models for which exact algorithms of \cite{beskos:papaspiliopoulos:roberts:fearnhead:2006} are valid, with a linear complexity in $N$ in the best cases, or at worse in $N^2$.
